Study protocol

### 2021-11-23 Manuscript/S1.Protocol.Rmd
clean: rename and move check_classification_trends in another source file

Now the annotation file is ready for the manual classification records.
The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
We suggest manually labelling an **initial training set** of 250 records, which should be sufficient if a minimum ~20% positivity rate is present (see the section about model hyperparameter optimisation)./
The function `check_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./

>>>>

Now the annotation file is ready for the manual classification records.
The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
We suggest manually labelling an **initial training set** of 250 records, which should be sufficient if a minimum ~20% positivity rate is present (see the section about model hyperparameter optimisation)./
The function `plot_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./
